\chapter{Conclusion}

This report presented \textbf{Event Blinker}, a comprehensive real-time event discovery platform that bridges the gap between event organizers and attendees through three key innovations: geospatial map-based event discovery, an AI-powered virtual concierge, and a peer-to-peer ride-sharing ecosystem.

The project was built on a robust, production-grade technology stack comprising:
\begin{itemize}[noitemsep]
    \item \textbf{Backend:} Node.js/Express.js with 11 API route modules (3,500+ lines of backend logic).
    \item \textbf{Database:} PostgreSQL with PostGIS extension, 12+ tables, 14+ spatial/performance indexes.
    \item \textbf{Mobile App:} React Native (Expo) with 10 screens and Zustand state management.
    \item \textbf{Web Portal:} React.js/Vite with 7 pages for organizer management.
    \item \textbf{Real-Time:} Socket.io with 10+ event types for chat and ride coordination.
    \item \textbf{AI:} LLAMA 3.3 via OpenRouter with 5-model fallback for high availability.
\end{itemize}

\noindent The project has successfully demonstrated:
\begin{enumerate}
    \item \textbf{Real-Time Geospatial Discovery:} Efficient map-based event browsing using PostGIS spatial queries with sub-200ms response times and GiST indexing.
    \item \textbf{Context-Aware AI Assistance:} \textbf{Blinker AI} provides event-specific, culturally localized responses by injecting live database context into LLM prompts, with multi-model fallback ensuring $>$95\% uptime.
    \item \textbf{Integrated Ride-Sharing:} A novel feature combining Haversine distance calculation, NPR dynamic pricing, 3-step verified driver registration, and Socket.io-based real-time ride coordination.
    \item \textbf{Live Social Engagement:} Socket.io-powered real-time chat with AI bot integration, event likes, and attendance check-ins.
    \item \textbf{Comprehensive Admin Control:} Multi-layer verification system for organizers, events, riders, and driver licenses through both API and standalone admin portal.
\end{enumerate}

Key challenges---including PostGIS query optimization, Socket.io cross-platform compatibility, AI hallucination mitigation, database schema evolution, and mobile state persistence---were addressed through iterative design, careful indexing, and robust fallback strategies.

Looking ahead, the platform will be enhanced with in-app payment integration (Khalti/Esewa), real-time GPS ride tracking, AI-powered event recommendations, push notifications, QR-code ticketing, and an iOS release. \textbf{Event Blinker} establishes a strong, scalable foundation for modern event-driven social networking in Nepal, demonstrating that locally-built technology can deliver world-class user experiences.