\chapter{Future Plan}

While the current version of \textbf{Event Blinker} provides a robust, feature-complete event ecosystem, the following enhancements are planned:

\begin{enumerate}
    \item \textbf{In-App Payment Integration:} Integrate Khalti and Esewa payment gateways for digital ticket purchase and ride fare collection directly within the mobile app.
    
    \item \textbf{Real-Time GPS Ride Tracking:} Add live GPS tracking for rides so passengers can monitor their driver's location on the map in real-time, similar to Pathao/inDrive.
    
    \item \textbf{Event Recommendation Engine:} Implement a collaborative filtering algorithm based on user like history, check-in patterns, and Blinker AI interaction data to suggest personalized events.
    
    \item \textbf{Push Notifications:} Integrate Firebase Cloud Messaging (FCM) for event reminders, ride request alerts, and chat message notifications when the app is in the background.
    
    \item \textbf{Multilingual AI Support:} Upgrade Blinker AI with multilingual capabilities to handle Nepali-language queries natively using a fine-tuned Nepali-English bilingual model.
    
    \item \textbf{Organizer Verification Tiers:} Introduce ``Verified Organizer'' badges with tiered verification levels (basic, premium) to build user trust and ensure event quality.
    
    \item \textbf{Event Ticketing with QR Codes:} Generate unique QR-code-based digital tickets for paid events, with a scanning mechanism at the venue entrance.
    
    \item \textbf{Live Event Streaming:} Allow organizers to live-stream key moments from events to attract remote attendees and build event hype.
    
    \item \textbf{Advanced Analytics Dashboard:} Expand the organizer portal with heatmap visualizations of attendee locations, demographic breakdowns, and revenue tracking.
    
    \item \textbf{iOS Release:} Build and publish the iOS version of the mobile app using Expo's EAS Build service.
\end{enumerate}
