\chapter{Objective}

The objectives of \textbf{Event Blinker} are structured into primary and secondary goals:

\section{Primary Objectives}
\begin{enumerate}
    \item To build a highly responsive, real-time event discovery platform that allows users to find events based on their GPS location using interactive Mapbox GL maps with PostGIS-powered radius filtering.
    \item To develop a localized AI assistant (\textbf{Blinker AI}) using LLAMA 3.3 that answers platform-specific and event-specific queries with contextual grounding (venue, price, time data injected from the database).
    \item To create a peer-to-peer ride-sharing ecosystem with verified drivers, Haversine distance calculation, and NPR dynamic pricing across multiple vehicle categories (Motorcycle, Sedan, SUV).
    \item To provide event organizers with a robust web dashboard (React/Vite) offering event creation, real-time chat management, and engagement analytics.
\end{enumerate}

\section{Secondary Objectives}
\begin{enumerate}
    \item To implement comprehensive admin verification workflows for organizers, events, riders, and driver licenses.
    \item To enable real-time social engagement through Socket.io-powered live chat, event likes, and attendance check-ins.
    \item To ensure platform security through JWT authentication, bcryptjs password hashing, rate limiting, CORS protection, and parameterized SQL queries.
    \item To deploy the platform on cloud infrastructure (Render) with Docker support for consistent environments.
\end{enumerate}